Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
zhifei is done
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1617 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: supporting for the syntax-augmented machine translation (SAMT) grammar,
supporting mannual constraints in the input to constrain the decoding,  
semiring parsing for unified dynamic programming, hypergraph-based 
discriminative training for better feature engineering, visualization of the derivation
trees and hypergraphs, and a unified pipeline for MT experiments.
\end{abstract}

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
The initial release also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

The toolkit has then been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this report, we will describe the main new functions we have added into the 
toolkit, which include: supporting for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
supporting manual constraints in the input to constrain the decoding \cite{PBML-2010-Josua-transliteration},  
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP}, 
hypergraph-based discriminative training for better feature engineering \cite{oracle-extraction-naacl09}, 
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
and a unified pipeline for MT experiments \cite{Schwartz-wmt10-pipline}.

Below we give a short description for each of the new functions added.

@@

We have also implemented the average Peceptron algorithm and the forest-reranking \cite{zhifei-forest-reranking-galebook}.
Since the reference translation may not be in the hypergraph due to pruning or inherent
defficiency of the translation grammar, we need to use an {\em oracle translation} (i.e., the translation in
the hypergraph that is most simmilar to the reference translation) as a surrogate for training.
We implemented the {\em oracle extraction} algorithm described by \newcite{oracle-extraction-naacl09}
for this purpose.

>>>>

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: 
supporting for the syntax-augmented machine translation (SAMT) grammar,
supporting mannual constraints in the input to constrain the decoding,  
lattice parsing for dealing with input uncertainty,
semiring parsing for unified dynamic programming, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees and hypergraphs, 
and a unified pipeline for MT experiments.
\end{abstract}

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

The toolkit has then been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we will describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
supporting for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
supporting mannual constraints in the input to constrain the decoding \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified pipeline for MT experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

@@

We have also implemented the average Perceptron algorithm and the forest-reranking \cite{zhifei-forest-reranking-galebook}.
Since the reference translation may not be in the hypergraph due to pruning or inherent
defficiency of the translation grammar, we need to use an {\em oracle translation} (i.e., the translation in
the hypergraph that is most simmilar to the reference translation) as a surrogate for training.
We implemented the {\em oracle extraction} algorithm described by \newcite{oracle-extraction-naacl09}
for this purpose.
